OptiFit: a fast method for fitting amplicon sequences to existing OTUs

### 2021-06-23 paper/paper.Rmd
link citations & remove knit override

---
title: "OptiFit: a fast method for fitting amplicon sequences to existing OTUs"
date: '`r Sys.Date()`'
bibliography: references.bib
output:
  pdf_document:
    includes:
      in_header: preamble.tex
      before_body: head.tex
    fig_caption: yes
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs", output_format = "all") })
csl: msystems.csl
fontsize: 12pt
geometry: margin=1.0in
repository_url: https://github.com/SchlossLab/OptiFitAnalysis
params:
    snakemake: "none"
---

>>>>

---
title: "OptiFit: a fast method for fitting amplicon sequences to existing OTUs"
date: '`r Sys.Date()`'
bibliography: references.bib
link-citations: true
output:
  pdf_document:
    includes:
      in_header: preamble.tex
      before_body: head.tex
    fig_caption: yes
csl: msystems.csl
fontsize: 12pt
geometry: margin=1.0in
repository_url: https://github.com/SchlossLab/OptiFitAnalysis
params:
    snakemake: "none"
---
